---
title: "Project 471"
author: "Sophia Margareta Carayannopoulos"
date: "4/24/2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

all_coin_data = read.csv("all_coin_data.csv")

```

#Playing With Data

###All Levels:
```{r, echo=FALSE}

coins = levels(all_coin_data$Coin)

```

###Closing worth each day for a year.
```{r, AllCoinsSeries}
par(mfrow=c(2,5))
for (i in coins) {
  plot(y= all_coin_data$Close[which(as.character(all_coin_data$Coin) == i)], x = all_coin_data$Day.1[which(as.character(all_coin_data$Coin) == i)], main = i, type = 'b', pch = 'o', xlab="Day", ylab="closing ")
  
}

```
Group 1: Steem, augur, ethereum, ethereum classic: have similar shapes. They have this hump between 100 and 250

Group 2: Dash, litecoin, monero, maidsafecoin: have a lot more up and down

Group 3: nem and ripple: also have super similar shapes, having a peak between 100 and 200

##Function for graphing groups
```{r, basicFunctions, echo=FALSE}
Setting_Window<- function(x){
  if( x == 1){
    par(mfrow=c(1,1))
  } else if(x == 2){
    par(mfrow=c(1,2))
  } else if( x == 3){
    par(mfrow=c(1,3))
  }else{
      par(mfrow=c(ceiling(x/2),ceiling(x/2)))
  }
}

plot_dot_closing <- function(groups, range_values){
  Setting_Window(length(groups))
  
  for (i in groups) {
  plot(y = all_coin_data$Close[which(all_coin_data$Coin == i & all_coin_data$Day.1 >= range_values[1] & all_coin_data$Day.1 < range_values[2])], 
       x = all_coin_data$Day.1[which(all_coin_data$Coin == i & all_coin_data$Day.1 >= range_values[1] & all_coin_data$Day.1 < range_values[2])], main = paste("Closing:", i), type = 'b', pch = 'o', xlab= "day", ylab = "Quantity")
  }
}

plot_dot_Total_Coin_Number_Comments <- function(groups, range_values){

  Setting_Window(length(groups))
  
  for (i in groups) {
      plot(y= all_coin_data$Total_Number_Coin_Comments[which(all_coin_data$Coin == i & all_coin_data$Day.1 >= range_values[1] & all_coin_data$Day.1 < range_values[2])], 
       x = all_coin_data$Day.1[which(all_coin_data$Coin == i & all_coin_data$Day.1 >= range_values[1] & all_coin_data$Day.1 < range_values[2])], main = paste("Total Number Coin Comments", i), type = 'b', pch = 'o', xlab= "day", ylab = "Quantity")
  }

  
}

plot_dot_Total_Coin_Number_Submissions_FOMO <- function(groups, range_values){
  Setting_Window(length(groups))
  for (i in groups) {
      plot(y= all_coin_data$Total_Coin_Submissions_Num_Fomo[which(all_coin_data$Coin == i & all_coin_data$Day.1 >= range_values[1] & all_coin_data$Day.1 < range_values[2])], 
       x = all_coin_data$Day.1[which(all_coin_data$Coin == i & all_coin_data$Day.1 >= range_values[1] & all_coin_data$Day.1 < range_values[2])], main = paste("Total Number Coin Submission FOMO", i), type = 'b', pch = 'o', xlab= "day", ylab = "Quantity")
  }
  
}

plot_dot_Total_Coin_Number_Submissions_FUD <- function(groups, range_values){
  Setting_Window(length(groups))
    
  for (i in groups) {
      plot(y= all_coin_data$Total_Coin_Submissions_Num_Fud[which(all_coin_data$Coin == i & all_coin_data$Day.1 >= range_values[1] & all_coin_data$Day.1 < range_values[2])], 
       x = all_coin_data$Day.1[which(all_coin_data$Coin == i & all_coin_data$Day.1 >= range_values[1] & all_coin_data$Day.1 < range_values[2])], main = paste("Total Number Coin Submissions FUD", i), type = 'b', pch = 'o', xlab= "day", ylab = "Quantity")
  }
}

plot_dot_Total_Coin_Number_Comments_FOMO <- function(groups, range_values){
  Setting_Window(length(groups))
  for(i in groups){
    plot( y = all_coin_data$Total_Coin_Comment_Num_Fomo[which(all_coin_data$Coin == i & all_coin_data$Day.1 >= range_values[1] & all_coin_data$Day.1 < range_values[2])],
          x =  all_coin_data$Day.1[which(all_coin_data$Coin == i & all_coin_data$Day.1 >= range_values[1] & all_coin_data$Day.1 < range_values[2])], main = paste("Quanity Comments FOMO", i), type = 'b', pch = 'o', xlab= "day", ylab = "Quantity")
  }
}

plot_dot_Total_Coin_Number_Comments_FUD <- function(groups, range_values){
  Setting_Window(length(groups))
  
  for(i in groups){
    plot( y = all_coin_data$Total_Coin_Comment_Num_Fomo[which(all_coin_data$Coin == i & all_coin_data$Day.1 >= range_values[1] & all_coin_data$Day.1 < range_values[2])],
          x  = all_coin_data$Day.1[which(all_coin_data$Coin == i & all_coin_data$Day.1 >= range_values[1] & all_coin_data$Day.1 < range_values[2])], main = paste("Quanity Comments FUD", i), type = 'b', pch = 'o', xlab= "day", ylab = "Quantity")
  }
}

```

###Inspecting humps in first group
```{r, LookingAtG1}
Group_1 <- c(coins[1], coins[10], coins[3], coins[4])
plot_dot_closing(Group_1, c(100, 250))
```

Seems that there is peaks in between 150 days and 200

```{r, continue_G1}
plot_dot_closing(Group_1, c(150, 200))
```

Looking at these graphs something is definitely going on between days 160 and 180

```{r, continue2_G1}
plot_dot_closing(Group_1, c(160, 175))
```
###Inspceting humps in the second group
```{r, LookingG2}
Group_2 <- c(coins[2], coins[5], coins[7], coins[6])
plot_dot_closing(Group_2, c(200, 300))
```
Definitely something between 220 and 280 for these coins. interesting that this is at completely different time then group 1.

```{r, continue_G2}
plot_dot_closing(Group_2, c(220,280))
```
okay looking at these closer it seems like we should inspect between 230 and 250
```{r, continue2_G2}
plot_dot_closing(Group_2, c(230, 250))
```
From here it seems that there is something going on with day 240ish, there seems to be a change or something happening in particular

###Looking through group 3
```{r, LookingG3}
Group_3 = c()
for( i in coins){
  if(!(i %in% Group_1) & !(i %in% Group_2)){
    Group_3 = c(Group_3, i)
  }
}

plot_dot_closing(Group_3, c(1, 365))
par(mfrow=c(2,1))
plot_dot_closing(Group_3, c(100, 200))
plot_dot_closing(Group_3, c(120, 180))
plot_dot_closing(Group_3, c(120, 150))
```
So once again we have found a special hump. 


##SUMMARY AFTER LOOKING AT 3 GROUPS

They each have their own particular days where closing coin value spikes up. None of them over lap or by very little if at all. Things to look into from here. Is there any expertise as to why these coins are grouped like this (meanig why do they have similar distributions) Also did anything else peak during that time? Anything else change out of the ordinary?

###Looking At Comments in General.
```{r, Comments}
mean(all_coin_data$Total_Number_Comments)
median(all_coin_data$Total_Number_Comments)
hist(all_coin_data$Total_Number_Comments )

plot(x = all_coin_data$Day.1, y = all_coin_data$Total_Number_Comments)
```

We see that in general that the comments have an upward trend in general. However we are able to seee two bumps, one between 100-200 and the other is between 200 -300. These could possibly line up with the bumps we saw in the above 3 groups. We will explore each of these groups individually.

#100-200 Hump
```{r, LookingHump1}
par(mfrow=c(2,2))
plot(x = all_coin_data$Day.1[which(all_coin_data$Day.1 >= 100 & all_coin_data$Day.1 < 200)], y = all_coin_data$Total_Number_Comments[which(all_coin_data$Day.1 >= 100 & all_coin_data$Day.1 < 200)], ylab= "comments", xlab = "day")

plot(x = all_coin_data$Day.1[which(all_coin_data$Day.1 >= 140 & all_coin_data$Day.1 < 200)], y = all_coin_data$Total_Number_Comments[which(all_coin_data$Day.1 >= 140 & all_coin_data$Day.1 < 200)], ylab= "comments", xlab = "day")

plot(x = all_coin_data$Day.1[which(all_coin_data$Day.1 >= 160 & all_coin_data$Day.1 < 200)], y = all_coin_data$Total_Number_Comments[which(all_coin_data$Day.1 >= 160 & all_coin_data$Day.1 < 200)], ylab= "comments", xlab = "day")

plot(x = all_coin_data$Day.1[which(all_coin_data$Day.1 >= 160 & all_coin_data$Day.1 < 180)], y = all_coin_data$Total_Number_Comments[which(all_coin_data$Day.1 >= 160 & all_coin_data$Day.1 < 180)], ylab= "comments", xlab = "day")
```
Once we get to the 160-180 it is harder to see that hump, but before that you can definitely see the hump. Makes me believe something happened in those days. So we will inspect 160-180. This is lines up with Group_1. So let's look as to what is going on.

#What type of comments
```{r, typesCommentsHump1, echo=FALSE}
par(mfrow=c(2,1))
plot(all_coin_data$Day.1, all_coin_data$Total_Number_Comments, ylab= "comments", xlab = "day", main =  "Total Number Comments")
plot(all_coin_data$Day.1[which(all_coin_data$Day.1 >= 160 & all_coin_data$Day.1 < 180)], all_coin_data$Total_Number_Comments[which(all_coin_data$Day.1 >= 160 & all_coin_data$Day.1 < 180)], ylab= "comments", xlab = "day", main =  "Total Number Comments 160-180")

plot_dot_Total_Coin_Number_Comments(Group_1, c(100,200))
```
Oh you can totoally see that the comments for that time in all those coins. So maybe # comments means something

Let's start looking at comments more specifically.
```{r, LookingCommentsSpecifics, echo=FALSE}

plot(x = all_coin_data$Day.1, y=all_coin_data$Total_Coin_Comment_Num_Fomo, ylab= "Day", xlab="Quantity", main= "FOMO comments all coins")
cat("So Fomo looks like is increasing exponetially. ")

plot_dot_Total_Coin_Number_Comments(Group_1, c(1,365))
plot_dot_Total_Coin_Number_Comments_FOMO(Group_1, c(1,365))
plot_dot_Total_Coin_Number_Comments_FUD(Group_1, c(1,365))

plot_dot_Total_Coin_Number_Comments_FOMO(Group_1, c(160,180))
plot_dot_Total_Coin_Number_Comments_FUD(Group_1, c(160, 180))
cat("now let's expan the range a bit to see if anything suspicious happen days before after")

plot_dot_Total_Coin_Number_Comments_FOMO(Group_1, c(140, 200))
plot_dot_Total_Coin_Number_Comments_FUD(Group_1, c(140, 200))

all_coin_data[which(all_coin_data$Day.1 < 180 & all_coin_data$Day.1 > 150 & all_coin_data$Coin == "steem" & all_coin_data$Total_Coin_Comment_Num_Fomo == 1),"Day.1"]

all_coin_data[which(all_coin_data$Day.1 < 180 & all_coin_data$Day.1 > 150 & all_coin_data$Coin == "steem" & all_coin_data$Total_Coin_Comment_Num_Fud == 1),"Day.1"]


```
We see the humps of # comments also peaks at the same time their price peaks. 
Possible peaks at the 160-180 mark


Looking at Submissions in general and specifics
```{r, look}
plot_dot_Total_Coin_Number_Submissions_FOMO(Group_1, c(1,365))
plot_dot_Total_Coin_Number_Submissions_FUD(Group_1, c(1, 365))

plot_dot_Total_Coin_Number_Submissions_FOMO(Group_1, c(140, 200))
plot_dot_Total_Coin_Number_Submissions_FUD(Group_1, c(140, 200))

plot_dot_Total_Coin_Number_Submissions_FOMO(Group_1, c(160, 180))
plot_dot_Total_Coin_Number_Submissions_FUD(Group_1, c(160, 180))

mean(all_coin_data$Total_Coin_Number_Submissions[which(all_coin_data$Day.1 <= 200 & all_coin_data$Day.1 >= 180 & all_coin_data$Coin == "steem" )])
```
Definitely looking like those humps mean something. Fud Submissions seem to be about the coin seem to be as it starts to fall.


#200-300 Hump
```{r, LookingHump2, echo=FALSE}
#par(mfrow=c(2,2))
#plot(x = all_coin_data$Day.1[which(all_coin_data$Day.1 >= 200 & all_coin_data$Day.1 < 300)], y = all_coin_data$Total_Number_Comments[which(all_coin_data$Day.1 >= 200 & all_coin_data$Day.1 < 300)], ylab= "comments", xlab = "day")

#plot(x = all_coin_data$Day.1[which(all_coin_data$Day.1 >= 220 & all_coin_data$Day.1 < 280)], y = all_coin_data$Total_Number_Comments[which(all_coin_data$Day.1 >= 220 & all_coin_data$Day.1 < 280)], ylab= "comments", xlab = "day")

#plot(x = all_coin_data$Day.1[which(all_coin_data$Day.1 >= 230 & all_coin_data$Day.1 < 270)], y = all_coin_data$Total_Number_Comments[which(all_coin_data$Day.1 >= 230 & all_coin_data$Day.1 < 270)], ylab= "comments", xlab = "day")

#plot(x = all_coin_data$Day.1[which(all_coin_data$Day.1 >= 240 & all_coin_data$Day.1 < 260)], y = all_coin_data$Total_Number_Comments[which(all_coin_data$Day.1 >= 240 & all_coin_data$Day.1 < 260)], ylab= "comments", xlab = "day")
```
Once again, you see that the 20 day one you don't see that hump, but as soon as you widen the scope you can see that this is a hump.

After looking
##Fitting A Model
```{r, FittingPCR}
pcr.fit = pcr(Close~.-Day-High-Low-Open, data=all_coin_data, scale=TRUE,validation="CV")
pcr.fit
summary(pcr.fit)
validationplot(pcr.fit,val.type="MSEP")
pcr.fit$loadings
```

